Estimating duration in the presence of misclassification

### 2024-07-31 biology-data.tex
Christl p44 minor comment

The age groups used have varied slightly for different CIS analyses~\autocite[e.g.][]{pouwelsMRPvaccination,pouwelsCommunity,cisMethodsONS,houseInferring,walkerTracking}.
I will use the age groups: 0--11 (pre-school and primary school), 12--16 (compulsory secondary school), 17--25 (adolescents and young adults who may remain in formal education), 26--50 (younger working age adults), 51--70 (older working age adults), and 71+ (elderly).

>>>>

The age groups used have varied slightly for different CIS analyses~\autocite[e.g.][]{pouwelsMRPvaccination,pouwelsCommunity,cisMethodsONS,houseInferring,walkerTracking}.
I will use the age groups: 0--11 years old (pre-school and primary school), 12--16 years old (compulsory secondary school), 17--25 years old (adolescents and young adults who may remain in formal education), 26--50 years old (younger working age adults), 51--70 years old (older working age adults), and over 71 years old (elderly).
